Cyclist video evidence of road traffic offences: Preliminary analysis of Operation Snap data and suggestions for a research agenda

### 2024-04-22 paper.qmd
Add abstract

>>>>

This study uses data from Operation Snap (Op Snap), the UK police’s national system to receive road users’ video evidence of road traffic offences.
Data from one police force area for three calendar years, from its launch in 2021 (N= 18,363 records) is analysed.
34.4% were submitted by cyclists (n=6,312).
69% of records resulted in an offence being registered and of those and 63% were for driving ‘without reasonable consideration to others’ or ‘without due care and attention’.
Three quarters (75.2%) resulted in the recommended disposal of an educational course (including conditional offers), a quarter in no further action, and fewer than 1% for court appearance.
A preliminary research agenda using Op Snap data is outlined.
In the first instance, comparative analysis of submission type, source, hotspot locations, and case disposal should be undertaken at national, regional and local levels, replicating the findings of this study.
Studies of disposal-related decision-making and the role of factors such as video quality and supporting evidence might identify good practice.
Research into video content, offence concentration, recidivism, repeat submitters of evidence, and case progression including court cases, hold significant potential to inform policy and practice locally, nationally and internationally.
